Trail Saving on Backtrack

### 2020-02-19 paper.tex
notes and useful papers

\section{Introduction}
\note{Fix later---also \cite{DBLP:journals/jsat/TakRH11} can't be
  first use of trail savings?}

>>>>

\section{Introduction}
\textbf{Overall message of the paper.}
\begin{enumerate}
\item Formalism for understanding a more general form of trail savings
    which caches a copy of the trail that is backtracked over, and
    verifying how it exploited soundly.

\item Potential advantages over chronological backtracking.  Literals
    remain at the correct level, supports the solver having more
    freedom in its decisions.

\item Potential advantages of techique (1) increase in efficiency of
    propagation, (2) the new uses of the cached information.

\item Potential disadvantage. Reasons are recycled, in some circumstances
    new reasons might be better. We show in a simple experiment that
    this effect can occur.

\item Techique captures most of the positive effects of
    non-chronological backtracking in a simpler to implement way. It
    also preserves the simpler standard structure of CDCL
    solvers. Already provides some advantages for current SAT
    solvers. The ideas also have the potential for further
    exploitation. Lookahead for conflicts seems to be beneficial, and
    potentially if better discrimatory measures could be developed for
    reason clauses we could also better determine whether or not to
    use the cached information.. 
\end{enumerate}

\note{Fix later---also \cite{DBLP:journals/jsat/TakRH11} can't be
  first use of trail savings?}

\note{Reusing the Assignment Trail in CDCL Solvers: restart to level
  $i$ where the next decision has a higher score than the decision at
  level $i$ and a lower score than all decisions at level $j$ for
  $j< i$.

  They argum changes to reason clauses don't make much difference, but
  that was with minisat, before metrics for clause quality were in place in sat solvers.

  The savings for Luby-100 (used in minisat) were about 1\%}
